\documentclass{article}
%\usepackage{hyperref}

\title{Planned Integration for \textbf{Version 3.0}}

\date{\today}

\begin{document}

\maketitle
To achieve unification and completion of theory, algorithm and implementation for all the essential components involved. 

\section{Theory}
\subsection{A Unified Theory for the Roles of Noises (Sam, Druv)}
That explains memorization and generalization. That is to clarify and elucidate necessary and sufficient conditions for correctly learning the support manifold of a low-dimensional distribution up to certain precision. That is in terms of the minimal number of samples and the optimal learning strategies,  say via denoising and diffusion. The theory should clarify the related roles of compression (outside the support manifold) and percolation (within the support manifold). 


\section{Unified Architectures and Algorithms }
\subsection{Causal Continuously Learning Architectures (Druv, Ziyang)}
A hierarchical and distributed closed-loop architecture. (This is closed associated with the previous and the next topics...)

\subsection{Online Optimization Strategies (Ziyang, Druv)}
That eliminates BP. 

\section{Applications and Unified Implementation }
\subsection{Learning Distribution of Control Policies (Brent, Tianzhe, Feng)} 
How to unify tasks-related reward (in the setting of RL/OC) and other constraints (observations) together with the (prior) low-dimensional support of data. (Computationally there should be unified framework for all these).
\subsection{Learning Full 3D/4D Distributions from Stereo Observations (Chenyu, Bingbing, Tianxin, Ruike)}

\end{document}